Stepwise Multiple Regressions

### 2021-02-10 Stepwise Multiple Regressions.Rmd

@@

>>>>

```{r}
#Plots

ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```

@@

summary(m1_crust_model_dose)

ggPredict(m1_crust_model_dose,colorn=100,jitter=TRUE, interactive = FALSE, digits = 3, se = FALSE)

```{r}
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```
```{r}
#alternative method using ggpredict
require(ggeffects)
require(ggdark)
require(ggsci)
ggpredict(m1_crust_model_dose)
df <- ggpredict(m1_crust_model_dose, se = TRUE)
df <- ggpredict(m1_crust_model_dose,terms=c("logdose.mg.L.master", "size.length.um.used.for.conversions"))

#note that faceting works best with discrete variable as interactive term
ggplot(df, aes(x = x, y = predicted, colour = group)) +
  geom_line() +
  geom_ribbon( aes(ymin = conf.low, ymax = conf.high, fill = group, color = NULL), alpha = .15) +
  facet_wrap(~.) +
  dark_theme_bw() +
  scale_color_tron()
```

```{r}
#alt method
plot(df, facet = TRUE)
```

## Discrete predictor and dose
```{r, echo = FALSE}
#Select the columns that we want to feed into the model for simplicity
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, size_f)) %>% 
  drop_na()

#Fit the full model
m1_crust_model_discrete <- glm(effect_10 ~ logdose.mg.L.master * size_f, data = m1_crust, na.action = "na.exclude", family = "binomial")

summary(m1_crust_model_discrete)
```
Plot.
```{r}
discrete <- ggpredict(m1_crust_model_discrete,terms = c("logdose.mg.L.master", "size_f"))
plot(discrete, facet = TRUE, add.data = TRUE)
```
### Survival package
```{r}
#include time
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, size_f, exposure.duration.d)) %>% 
  drop_na()

require(survival)
survival <- survival::coxph(survival::Surv(exposure.duration.d, effect_10) ~ logdose.mg.L.master + size_f, data = m1_crust)
#cumulative hazard
cumHaz <- ggpredict(survival,terms = c("logdose.mg.L.master", "size_f"), type = "cumhaz")
plot(cumHaz, facet = TRUE, add.data = TRUE, colors = "flat")
```
```{r}
#survival probability over time
pr <- ggpredict(survival, c("logdose.mg.L.master", "size_f"), type = "surv")
plot(pr, colors = "social")
```
